Sparse Function-space Representation \\ of Neural Networks

### 2023-05-14 paper/main.tex
rewrite 2.1 first draft done

A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}. The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function  
% $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ 
with the Generalized Gaussian-Newton approximation (GGN). 
Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}) = \Jac{\weights_*}{\mathbf{x}} \, \weights$, where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian at the MAP. Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.

In this paper, we are concerned with learning the posterior $q(\vf)$ directly in the function space, instead of $q(\vw)$. We choose to use a Gaussian process, an extension of the multivariate normal that characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance  (or kernel) function $\kappa(\cdot,\cdot)$. We aim to derive these two functions based on the neural network to then build the Gaussian process posterior. Gaussian distributions remain tractable under learn transformations. Therefore, a linear function with respect to its parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows: \todo{this part needs to be improved the linear function pops out of nowhere}
\begin{equation} \label{eq:weight_func}
g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
\end{equation}

>>>>

A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}. The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function  
% $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ 
with the Generalized Gaussian-Newton approximation (GGN). 
Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}_i) = \Jac{\weights_*}{\mathbf{x}_i} \, \weights$, where $\Jac{\weights}{\mathbf{x}_i} \coloneqq \nabla_\weights f(\mathbf{x}_i)^\top \in \R^{C \times P}$ is the Jacobian at the MAP. Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.

Recent work \citep{khan2019approximate,maddox2021fast} shows that linearizing approximations in the weight space lead to function space equivalent approximations. As our goal is to build a sparse functional representation of a neural network, a starting point is the non-sparse  $q(\vf)$ function space posterior approximation. We choose to use a Gaussian process, as is typical, an extension of the multivariate normal that characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance  (or kernel) function $\kappa(\cdot,\cdot)$. Thus, we need these two functions based on the neural network to build the Gaussian process posterior. Gaussian distributions remain tractable under linear transformations. Therefore, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx_i) \, \vw \implies \mu(\vx_i) = 0 \quad \kappa(\mathbf{x}_i, \mathbf{x}_i') = \frac{1}{\delta} \phi(\vx_i)^\top \phi(\vx_i)
\end{equation}
